### 2016-01-31 inputs/abstract.tex
phrasing

\begin{abstract}
Genotyping-by-sequencing (GBS) is a rapid and cost-effective genome-wide 
genotyping technique applicable whether a reference genome is available 
or not. Due to the cost-coverage trade-off, however, GBS typically produces 
large amounts of missing marker genotypes, whose imputation becomes therefore 
both challenging and critical to ensure reliability of later analyses.\\
In this work, the performance of four general imputation methods (K-Nearest 
Neighbors, Random Forest, Singular Value Decomposition, and Mean Value)
and one genotype-specific method (``Beagle'') were measured 
on GBS data from alfalfa (\emph{Medicago sativa}, autotetraploid, heterozygous, 
without reference genome) and 
rice (\emph{Oryza sativa}, with reference genome, 100\% homozygous). Benchmarks 
consisted in progressive data filtering for marker call-rate (up to 70\%) and increasing 
proportions (up to 20\%) of known genotypes “masked” for imputation. The 
relative performance was measured as the total proportion of correctly imputed 
genotypes, globally and within each genotype class (two homozygotes in rice, 
two homozygotes and one heterozygote in alfalfa). Imputation efficiency was 
measured with computation times.\\
In general imputation accuracy was robust to increasing 
missing rates, and consistently higher in rice than in alfalfa. Accuracy 
was as high as 90-100\% for the major (most frequent) homozygous genotype, but dropped 
to 80-90\% (rice) and below 30\% (alfalfa) on the minor homozygous genotype. 
Beagle was the best performing method, both accuracy- 
and time-wise, when using a reference genome; when no reference 
genome was available, KNNI and RFI gave the highest accuracies, with KNNI 
being much faster.

>>>>

\begin{abstract}
Genotyping-by-sequencing (GBS) is a rapid and cost-effective genome-wide 
genotyping technique applicable whether a reference genome is available 
or not. Due to the cost-coverage trade-off, however, GBS typically produces 
large amounts of missing marker genotypes, whose imputation becomes therefore 
both challenging and critical to ensure reliability of later analyses.\\
In this work, the performance of four general imputation methods (K-Nearest 
Neighbors, Random Forest, Singular Value Decomposition, and Mean Value)
and one genotype-specific method (``Beagle'' and \textcolor{red}{FILLIN}) were measured 
on GBS data from alfalfa (\emph{Medicago sativa}, autotetraploid, heterozygous, 
without reference genome) and 
rice (\emph{Oryza sativa}, with reference genome, 100\% homozygous). Benchmarks 
consisted in progressive data filtering for marker call-rate (up to 70\%) and increasing 
proportions (up to 20\%) of known genotypes “masked” for imputation. The 
relative performance was measured as the total proportion of correctly imputed 
genotypes, globally and within each genotype class (two homozygotes in rice, 
two homozygotes and one heterozygote in alfalfa). Imputation efficiency was 
measured with computation times.\\
In general imputation accuracy was robust to increasing 
missing rates, and consistently higher in rice than in alfalfa. Accuracy 
was as high as 90-100\% for the major (most frequent) homozygous genotype, but dropped 
to 80-90\% (rice) and below 30\% (alfalfa) on the minor homozygous genotype. 
Beagle was the best performing method, both accuracy- 
and time-wise, when using a reference genome; when no reference 
genome was available, KNNI and RFI gave the highest accuracies, with KNNI 
being much faster.

### 2016-01-31 inputs/introduction.tex
phrasing

the different imputation methods was assessed in terms of the 
accuracy achieved and the computation time required. Not only the total imputation accuracy was measured, but also the accuracy of imputing the different genotype classes (major and minor homozygotes, heterozygotes).\\

>>>>

the different imputation methods was assessed in terms of  
accuracy and computation time. Accuracy was measured in terms
of gross fraction of correctly imputed genotypes, and within
genotype classes (major/minor homozites and heterozigotes, when present).
